---
output:
  html_document: default
  word_document: default
---
---
title: "histogram without na"
output:
  word_document: {r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

##Loading Data

setwd("D:/Private/Data_Sceince/Reproducible Search/Projects/repdata_data_activity")
data<-read.csv("activity.csv")
##Preprocessing of data
data$date<-as.Date(data$date)
##Histogram of total number of steps taken on each day
no_of_steps<-aggregate(data$steps,by=list(data$date),FUN=sum,na.rm=TRUE) 
```

```{r}
hist(no_of_steps$x, 
      breaks=seq(from=0, to=25000, by=2500),
      col="yellow", 
      xlab="Total number of steps", 
      ylim=c(0, 20), 
      main="total number of steps taken each day")
```

```{r}
##Mean and median number of steps 
mean(no_of_steps$x)
## [1] 9354.23
median(no_of_steps$x)
## [1] 10395
```

```{r}
##Time Series Plot
avg_steps<-aggregate(data$steps,by=list(data$interval),FUN=mean,na.rm=TRUE)

colnames(avg_steps)<-c("interval","steps")


library(ggplot2)
ggplot(aes(x=interval,y=steps),data=avg_steps)+geom_line()
```

```{r}
## Average 5 minute interval
avg_steps[avg_steps$steps==max(avg_steps$steps),1]

## [1] 835

##Imputing NA

sum(is.na(data$steps))
## [1] 2304

##Replace NA values with the mean of the steps

data$steps[is.na(data$steps)]<-mean(data$steps,na.rm=TRUE)
```

```{r}
##Histogram with Repaced NA values

sum_steps<-aggregate(data$steps,by=list(data$date),FUN=sum,na.rm=TRUE) 

hist(sum_steps$x, 
      breaks=seq(from=0, to=25000, by=2500),
      col="yellow", 
      xlab="Total number of steps", 
      ylim=c(0, 30), 
      main=" steps taken each day\n(NA replaced by mean)")

```

```{r}
##Mean and median number of steps taken each day after replacing NA values with mean

mean(sum_steps$x)
## [1] 10766.19
median(sum_steps$x)
## [1] 10766.19      

##  date into weekdays

data$days=tolower(weekdays(data$date))

##days into weekend and weekdays

data$day_type<-ifelse(data$days=="saturday"|data$days=="sunday","weekend","weekday")

```

```{r}
## mean steps  on weekend or weekday 

avg_steps<-aggregate(data$steps,by=list(data$interval,data$day_type),FUN=mean,na.rm=TRUE)

colnames(avg_steps)<-c("interval","day_type","steps")

## Create panel plot between average steps and interval

ggplot(aes(x=interval,y=steps),data=avg_steps)+geom_line()+facet_wrap(~avg_steps$day_type)
```